Last glacial cycle glacier erosion potential in the Alps

### 2021-02-15 articles/erosion/alps-erosion.tex
Improve figure placement in the text.
Fix data dois to newer versions, add video links.

    \begin{figure*}[ht]
      \centerline{\includegraphics{alpero_landscape}}
      \caption{%
        Alpine glacial erosion landscape diversity.
        \textbf{(a)} Piedmont overdeepening of Lake Constance, ca.~10x50\,km.
        \textbf{(b)} Glacial trough of Lauterbrunnental, ca.~1x10\,km.
        \textbf{(c)} Mountain cirque of Ch\"uebodengletscher, ca.~1x1\,km.}
      \label{fig:landscape}
    \end{figure*}

@@

    \begin{figure*}[ht]
      \centerline{\includegraphics{alpero_cumulative}}
      \caption{%
        \textbf{(a)} Modelled cumulative (time-integrated) glacial erosion
          potential over the last glacial cycle.
        \textbf{(b)} Modelled total ice volume in centimetres of sea-level
          equivalent (cm~s.l.e., black), annual (domain-integrated) erosion
          volume (light brown) and 1-ka running mean (dark brown). Shaded gray
          areas indicate the timing for MIS~2 and~4
          \citep{Lisiecki.Raymo.2005}.}
        \label{fig:cumulative}
    \end{figure*}

@@

    \begin{figure}[ht]
      \centerline{\includegraphics{alpero_evolution}}
      \caption{%
        Modelled annual (domain-integrated) erosion volume (light brown) and 1-ka
        running mean (dark brown) in relation to modelled total ice volume in
        centimetres of sea-level equivalent.}
      \label{fig:evolution}
    \end{figure}

@@

    \begin{figure*}[ht]
      \centerline{\includegraphics{alpero_transects}}
      \caption{%
        \textbf{(a, b, c)} Modelled instantaneous erosion rate of the Rhine
          Glacier for selected post-Last Glacial Maximum ages.
        \textbf{(d)} Interpolated instantaneous erosion rate along a Rhine
          Glacier transect for the entire last glacial cycle (upper panels
          dashed line).}
      \label{fig:transects}
    \end{figure*}

    \begin{figure*}[ht]
      \centerline{\includegraphics{alpero_hypsogram}}
      \caption{%
        \textbf{(a)} Modelled erosion rate ``hypsogram'', showing the geometric
          mean of (non-zero) modelled erosion rates in 10-m elevation bands
          across the entire model domain and its time evolution. The histogram
          to the side shows the distribution of topography in the model domain.
        \textbf{(b)} Same as Fig.~\ref{fig:cumulative}b.}
      \label{fig:hypsogram}
    \end{figure*}

@@

    \begin{figure*}[ht]
      \centerline{\includegraphics{alpero_sensitivity}}
      \caption{%
        Modelled cumulative glacial erosion potential over the last glacial
        cycle without \textbf{(a, b, c)} and with \textbf{(d, e, f)}
        paleo-precipitation corrections, and using three different
        palaeo-temperature histories \citep[see][]{Seguinot.etal.2018}.}
      \label{fig:sensitivity}
    \end{figure*}

@@

    \begin{figure*}[ht]
      \centerline{\includegraphics{alpero_powerlaws}}
      \caption{%
        Modelled cumulative (time-integrated) glacial erosion potential for
        three different erosion laws published by
        \textbf{(a)} \citet{Koppes.etal.2015},
          ${5.2 \times 10^{-8} u_\mathrm{b}^{2.34}}$ (same as
          Fig.~\ref{fig:cumulative}a but with a different colour scale),
        \textbf{(b)} \citet{Herman.etal.2015},
          ${2.7 \times 10^{-7} u_\mathrm{b}^{2.02}}$,
        \textbf{(c)} \citet{Humphrey.Raymond.1994},
          ${1 \times 10^{-4} u_\mathrm{b}^{1}}$, and
        \textbf{(d)} \citet{Cook.etal.2020},
          ${1.665 \times 10^{-1} u_\mathrm{b}^{0.6459}}$.
        \textbf{(e-h)} Corresponding modelled cumulative glacial erosion
          potential along a Rhine Glacier transect (upper panels dashed line), and
        \textbf{(i-l)} corresponding modelled evolution of annual
        (domain-integrated) erosion volume (light brown) and 1-ka
        running mean (dark brown) in relation to modelled total ice volume in
        centimetres of sea-level equivalent (as in Fig.~\ref{fig:evolution}a).}
      \label{fig:powerlaws}
    \end{figure*}

@@

\codedataavailability{%
    PISM is available as open-source software (http://pism-docs.org).
    Time and domain-aggregated erosion variables such as used in the figures is
    available for the four presented erosion power-laws
    (\doi{10.5281/zenodo.4495419}). Other model output variables were
    previously made available (\doi{10.5281/zenodo.1423160},
    \doi{10.5281/zenodo.1423176}).}

>>>>

    \begin{figure*}
      \centerline{\includegraphics{alpero_landscape}}
      \caption{%
        Alpine glacial erosion landscape diversity.
        \textbf{(a)} Piedmont overdeepening of Lake Constance, ca.~10x50\,km.
        \textbf{(b)} Glacial trough of Lauterbrunnental, ca.~1x10\,km.
        \textbf{(c)} Mountain cirque of Ch\"uebodengletscher, ca.~1x1\,km.}
      \label{fig:landscape}
    \end{figure*}

@@

    \begin{figure*}
      \centerline{\includegraphics{alpero_cumulative}}
      \caption{%
        \textbf{(a)} Modelled cumulative (time-integrated) glacial erosion
          potential over the last glacial cycle.
        \textbf{(b)} Modelled total ice volume in centimetres of sea-level
          equivalent (cm~s.l.e., black), annual (domain-integrated) erosion
          volume (light brown) and 1-ka running mean (dark brown). Shaded gray
          areas indicate the timing for MIS~2 and~4
          \citep{Lisiecki.Raymo.2005}.}
        \label{fig:cumulative}
    \end{figure*}

@@

    \begin{figure}
      \centerline{\includegraphics{alpero_evolution}}
      \caption{%
        Modelled annual (domain-integrated) erosion volume (light brown) and 1-ka
        running mean (dark brown) in relation to modelled total ice volume in
        centimetres of sea-level equivalent.}
      \label{fig:evolution}
    \end{figure}

@@

    \begin{figure*}
      \centerline{\includegraphics{alpero_transects}}
      \caption{%
        \textbf{(a, b, c)} Modelled instantaneous erosion rate of the Rhine
          Glacier for selected post-Last Glacial Maximum ages.
        \textbf{(d)} Interpolated instantaneous erosion rate along a Rhine
          Glacier transect for the entire last glacial cycle (upper panels
          dashed line).}
      \label{fig:transects}
    \end{figure*}

    \begin{figure*}
      \centerline{\includegraphics{alpero_hypsogram}}
      \caption{%
        \textbf{(a)} Modelled erosion rate ``hypsogram'', showing the geometric
          mean of (non-zero) modelled erosion rates in 10-m elevation bands
          across the entire model domain and its time evolution. The histogram
          to the side shows the distribution of topography in the model domain.
        \textbf{(b)} Same as Fig.~\ref{fig:cumulative}b.}
      \label{fig:hypsogram}
    \end{figure*}

@@

    \begin{figure*}
      \centerline{\includegraphics{alpero_sensitivity}}
      \caption{%
        Modelled cumulative glacial erosion potential over the last glacial
        cycle without \textbf{(a, b, c)} and with \textbf{(d, e, f)}
        paleo-precipitation corrections, and using three different
        palaeo-temperature histories \citep[see][]{Seguinot.etal.2018}.}
      \label{fig:sensitivity}
    \end{figure*}

@@

    \begin{figure*}[t]
      \centerline{\includegraphics{alpero_powerlaws}}
      \caption{%
        Modelled cumulative (time-integrated) glacial erosion potential for
        three different erosion laws published by
        \textbf{(a)} \citet{Koppes.etal.2015},
          ${5.2 \times 10^{-8} u_\mathrm{b}^{2.34}}$ (same as
          Fig.~\ref{fig:cumulative}a but with a different colour scale),
        \textbf{(b)} \citet{Herman.etal.2015},
          ${2.7 \times 10^{-7} u_\mathrm{b}^{2.02}}$,
        \textbf{(c)} \citet{Humphrey.Raymond.1994},
          ${1 \times 10^{-4} u_\mathrm{b}^{1}}$, and
        \textbf{(d)} \citet{Cook.etal.2020},
          ${1.665 \times 10^{-1} u_\mathrm{b}^{0.6459}}$.
        \textbf{(e-h)} Corresponding modelled cumulative glacial erosion
          potential along a Rhine Glacier transect (upper panels dashed line), and
        \textbf{(i-l)} corresponding modelled evolution of annual
        (domain-integrated) erosion volume (light brown) and 1-ka
        running mean (dark brown) in relation to modelled total ice volume in
        centimetres of sea-level equivalent (as in Fig.~\ref{fig:evolution}a).}
      \label{fig:powerlaws}
    \end{figure*}

@@

\codedataavailability{%
    PISM is available as open-source software (http://pism-docs.org).
    Time and domain-aggregated erosion variables such as used in the figures is
    available for the four presented erosion power-laws
    (\doi{10.5281/zenodo.4495419}). Other model output variables were
    previously made available (\doi{10.5281/zenodo.3604174},
    \doi{10.5281/zenodo.3604142}).}

\videosupplement{
    Animations made available online show the modelled glacier erosion rates
    (\url{https://vimeo.com/503162771}), and their evolving relationship with
    ice volume (\url{https://vimeo.com/512478926}) and bedrock
    altitude (\url{https://vimeo.com/512479008}).}
